A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-09-11 main.tex
remove double space

\subsection{ML Pipelines}
\label{ml_pipelines}
ML pipelines are often long-running and complex software tool-chains with many tunable hyper-parameters.
Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc,hydra,k8s}.
In general, a dataset is split into \textit{training} and \textit{test} sets.
The test set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users.
Since different hardware devices have differing amounts of ~\acrfull{vram}, the resulting models will have differing optimal configurations if both robustness and training cost are considered.
To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption. Likewise, Nvidia offers hardware that is marketed as either for training (\textit{e.g.}, v100 and p100) or only for inference (\textit{e.g.}, l4).

>>>>

\subsection{ML Pipelines}
\label{ml_pipelines}
ML pipelines are often long-running and complex software tool-chains with many tunable hyper-parameters.
Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc,hydra,k8s}.
In general, a dataset is split into \textit{training} and \textit{test} sets.
The test set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users.
Since different hardware devices have differing amounts of \acrfull{vram}, the resulting models will have differing optimal configurations if both robustness and training cost are considered.
To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption. Likewise, Nvidia offers hardware that is marketed as either for training (\textit{e.g.}, v100 and p100) or only for inference (\textit{e.g.}, l4).
